\section{Related Work}
\label{sec:related-work}

While there is a vast literature on automatically repairing or patching 
programs for specific properties (\eg null-dereferences, memory safety),
we focus on the most closely related work on providing feedback for novice 
errors.

\mypara{Example-Based Feedback} 
%
Recent work has looked at providing \emph{counterexamples} 
that show how a program went wrong, for type errors 
\cite{Seidel2016-ul} or for general correctness properties 
where the generated inputs show divergence from a reference 
implementation or other correctness oracle~\cite{Song_2019}.
In contrast, we provide feedback on how to fix the error.

\mypara{Fault Localization} Several authors have studied 
the problem of \emph{fault localization}, \ie winnowing down 
the set of locations that are relevant for the error, often 
using slicing \citep{Wand1986-nw,Haack2003-vc,Tip2001-qp,Rahli2015-tt},
counterfactual typing \citep{Chen2014-gd} or bayesian methods \citep{Zhang2014-lv}.
%
\textsc{Nate}~\citep{Seidel:2017} introduced the BOAT representation, 
and showed it could be used for accurate localization.
%
We aim to go beyond localization, into suggesting concrete 
\emph{changes} that novices can make to understand and fix 
the problem.

\mypara{Repair-model based feedback} 
%
\textsc{Seminal} \citep{Lerner2007-dt} \emph{enumerates} minimal fixes 
using an expert-guided heuristic search. 
%
The above approach is generalized to general correctness properties 
by \cite{singh2013} which additionally performs a \emph{symbolic} 
search using a set of expert provided \emph{sketches} that represent 
possible repairs. 
%
In contrast, \toolname learns a template of repairs 
from a corpus yielding higher quality feedback \S~\ref{sec:eval}.

\mypara{Corpus-based feedback}
%
\textsc{Clara} \citep{Gulwani_2018} uses code and execution traces 
to match a given incorrect program with a ``nearby'' correct solution 
obtained by clustering all the correct answers for a particular task.
The matched representative is used to extract repair expressions. 
%
Similarly, \textsc{Sarfgen} \citep{Wang_2018} focuses on structural 
and control-flow similarity of programs to produce repairs, by using 
AST vector embeddings to calculate distance metrics (to ``similar'' 
or ``nearby'' correct programs) more robustly.
%
While the above are data-driven, both \textsc{Clara} and \textsc{Sarfgen} 
assume there is a ``close'' correct sample in the corpus. 
%
In contrast, \toolname has a more general philosophy that 
\emph{similar errors have similar repairs}: we extract 
generic fix templates that can be applied to arbitrary 
programs whose errors (BOAT vectors) are similar.
%
The \textsc{Tracer} system \cite{TRACER2018} is closest 
in philosophy to ours, except that it focuses on single-line 
compilation errors for C programs, where it shows that 
NLP-based methods like sequence-to-sequence predicting 
DNNs can effectively suggest repairs, \eg \verb+scanf("%d", a)+ 
should be converted to \verb+scanf("%d", %a)+. 
%
We have found that \ocaml's relatively simple 
\emph{syntactic} structure but rich \emph{type} 
structure make token-level seq-to-seq methods 
quite imprecise \footnote{the strategy of 
\emph{deleting} offending statements 
suffices to ``repair'' C but yields ill-typed 
\ocaml} necessitating \toolname's higher-level 
semantic features and (learned) repair templates.


%
% \textsc{Hercules} \citep{Saha_2019} uses version history to  
% repair multiple program locations by using fault localization 
% to rank error locations and then generating repairs for each 
% location. 
% %
% However, it utilizes version history of a big codebase to find 
% such repairs, and uses that history to produce repairs that 
% modifies multiple program locations. 
% %
% \toolname attempts a different approach of multiple location
% repairing, by considering each candidate error location as independent from one
% another.
% 
%% While \textsc{Sarfgen} is still a data-driven approach it tries to
%% search for matching programs on the fly, using \toolname's approach can be similarly
%% seen as a per AST node embedding, which however we use in advance for training
%% predictive models, thus mitigating any extra cost on runtime.
%% 
%% that can be used to produce repairs. Despite the apparent
%% similarities, \toolname partitions similar fix patterns found in our dataset,
%% while \textsc{Clara} clusters whole student solutions. 
%% 
%% Additionally, \textsc{Clara} assumes that there is always 
%% a matching student solution in the dataset, while \toolname 
%% extracts generic fix templates can be applied to arbitrary 
%% programs. 
%% 
%% \textsc{Clara} also scales poorly in matching programs due
%% to the use of Integer Linear Programming, while \toolname's precomputation of
%% fix-template models makes final repairs more robust.

