\section{Template-Guided Repair Synthesis}
\label{sec:synthesis}
We use program synthesis to fully repair a program using predicted fix templates
and locations from our machine learning models. We present in
\S~\ref{sec:synthesis:local-synthesis} a synthesis algorithm for producing
\emph{local repairs} for a given program location. In
\S~\ref{sec:synthesis:location-rank}, we show how we use local repairs to repair
programs that may have \emph{multiple} error locations.

\lstMakeShortInline[mathescape=true]{|}

\subsection{Local Synthesis from Templates}
\label{sec:synthesis:local-synthesis}

\mypara{Enumerative Program Synthesis}
We utilize classic \emph{enumerative} program synthesis that is guided by a fix
template. Enumerative synthesis searches all possible expressions over a
language until a high-level specification is reached. In our case, we initially
synthesize independent \emph{local repairs} for a program that already captures
the user's intent. Therefore, the required specification is that the repaired
program is type-safe. However, if the users provide type signatures for their
programs, they can be used as a stricter specification.

Given a location $l$, a template $t$ and a maximum depth $d$,
\autoref{algo:local-repair-algo} searches over all possible expressions over
\lang that will satisfy those goals by generating a local repair that fills
$t$'s GAST with concrete variables, literals, functions \etc Our technique can
also reuse subexpressions $e$ at location $l$ for $t$'s concretization to
further optimize the search.

\input{local-repair.tex}

\mypara{Template-Guided Local Repair}
Using the \textsc{Repair} method (\autoref{algo:local-repair-algo}), we produce
local repairs $R$ for a given location $L$ of an erroneous program $P$.
\textsc{Repair} fills in a template $T$ based on the context-free grammar
$\lang$. It traverses the GAST of template $T$ from root node
downward, producing candidate local repairs of maximum depth $D$.

When a hole $\alpha \in T$ is found, the algorithm expands $T$'s GAST one more
level using $\lang$'s production rules $Q$. The production rules are considered
in a ranked order based on the subexpressions that already appear in the rest
of the template $T$ and program location $L$. Each rule is then applied to
template $T$, returning an \emph{instantiated} template $\hat{T}$, which is
inserted into the list of candidate local repairs $R$.

If node $\alpha$ is not a hole, terminals from the subexpressions at location
$L$, the program $P$ in general and the grammar $\lang$ are used to concretize
that node, depending on the $\repairLang$ terminal node $\alpha$. For each of
these template $T$ modifications, we insert an instantiated template $\hat{T}$
into $R$.
% $R$ is generated lazily in practice and the top-N can be requested for the user

\subsection{Ranking Error Locations}
\label{sec:synthesis:location-rank}

\mypara{Error Location Confidence}
Recall from \autoref{sec:templ-pred} that for each subexpression in a program's
type-error slice, $\Model$ generates a confidence score $\Conf$ for it being the
error location, and $\ModelT$ generates scores for the fix templates.

Our synthesis algorithm ranks all program locations based on their confidence
scores $\Conf$. For all locations in descending confidence score order, a fix
template is used to produce a local repair using
\autoref{algo:local-repair-algo}. Fix templates are considered in descending
order of confidence. Then expressions from the returned list of local repairs
$R$ replace the expression at the given program location. The procedure tries
the remaining repairs, templates, and locations until a type-correct program is
found.

Following \citep{Lerner2007-dt}, we allow our final local repairs to have
program holes $\_$ or abstracted variable $\hat{x}$ in them. However,
\autoref{algo:local-repair-algo} will prioritize the synthesis of complete
solutions. Abstract $\repairLang$ terms can have any
type when type-checking concrete solutions, similarly to \ocaml's |raise Exn|.

\mypara{Multiple Error Locations}
In practice, frequently more than one program location needs to be repaired. We
thus extend the above approach to fix programs with multiple errors. Let the
confidence scores $\Conf$ for all locations $L$ in the type error slice from our
error localization model $\Model$ be $(l_1, c_1), \dots, (l_k, c_k)$, where
$l_i$ is a program location and $c_i$ its error confidence score. We assume for
simplicity that the probabilities $c_i$ are independent. Thus the probability
that \emph{all} the locations $\{l_i \dots l_j\}$ need to be fixed is the
product $c_i \cdots c_j$. Therefore, instead of ranking and trying to find fixes
for single locations $l$, we use \emph{sets} of locations ($\{l_i\}, \{l_i,
l_j\}, \{l_i, l_j, l_k\}$, \etc), ranked by the products of their confidence
scores. For a given set, we use \autoref{algo:local-repair-algo} independently
for each location in the set and apply all possible combinations of local
repairs, looking again for a type-correct solution.
% In practice we only consider up to \emph{five} locations to be fixed
% simultaneously; any more than that takes too much time to generate and has too
% small a chance of leading to a good solution.

\lstDeleteShortInline{|}
